---
title: "Preliminary Report"
author: "Erik Westlund"
date: "June 13, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("bootstrap.R")
source("analysis/preliminary-analysis.R")
```

# Competence Mismatch

I've got the project coded up in a reproducible way using the restricted data. Here are preliminary results.

## Earned BA vs. Math-Reading Standardized Test Score Differences

Math-Reading difference is significant.

```{r}
summary(earned_ba_standardized_test_score_model)
exp(cbind(coef(earned_ba_standardized_test_score_model)))
```


## Earned BA vs. Math-Verbal SAT Score Differences

Math-Verbal difference is significant.

```{r}
summary(earned_ba_sat_score_model)
exp(cbind(coef(earned_ba_sat_score_model)))
```

## Transferred Colleges vs. Math-Reading Standardized Test Score Differences

Math-Reading difference is *not* significant.

```{r}
summary(transferred_colleges_standardized_test_score_model)
exp(cbind(coef(transferred_colleges_standardized_test_score_model)))
```


## Transferred Colleges  vs. Math-Verbal SAT Score Differences

Math-Verbal difference is *not* significant.

```{r}
summary(transferred_colleges_sat_score_model)
exp(cbind(coef(transferred_colleges_sat_score_model)))
```


## Applied to High Selective College vs. Math-Reading Standardized Test Score Differences

Math-Reading difference is significant.

```{r}
summary(applied_to_highly_selective_college_standardized_test_score_model)
exp(cbind(coef(applied_to_highly_selective_college_standardized_test_score_model)))
```


## Applied to High Selective College  vs. Math-Verbal SAT Score Differences

Math-Verbal difference is significant.

```{r}
summary(applied_to_highly_selective_college_sat_score_model)
exp(cbind(coef(applied_to_highly_selective_college_sat_score_model)))
```


## Grades Are Very Important vs. Math-Reading Standardized Test Score Differences

Math-Reading difference is *not* significant.

```{r}
summary(grades_very_important_standardized_test_score_model)
exp(cbind(coef(grades_very_important_standardized_test_score_model)))
```


## Grades Are Very Important  vs. Math-Verbal SAT Score Differences

Math-Verbal difference is *not* significant.

```{r}
summary(grades_very_important_sat_score_model)
exp(cbind(coef(grades_very_important_sat_score_model)))
```
